Reflections from reproductions

### 2024-12-10 pages/reflections.qmd
docs(reflections): redid summary graph and corrected callout colours

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  'List packages': [2, 3, 3, 0],
  'Provide versions': [0, 6, 2, 0],
  'Model in "runnable" format': [7, 0, 1, 0],
  'Can run some programmatically': [7, 0, 1, 0],
  '''Don't hard code scenario param.''': [3, 2, 2, 1],
  'Relative file paths': [5, 0, 0, 3],
  'Avoid duplication': [5, 0, 3, 0],
  'Sufficient comments': [1, 3, 4, 0],
  'If slow, state run time': [2, 2, 3, 1],
  'Provide scenario code': [1, 1, 5, 1],
  'Provide all required outputs': [3, 0, 5, 0],
  'Include correct parameters': [4, 2, 2, 0],
  'Provide all required parameters': [4, 0, 4, 0],
  'If not, clearly state in paper': [1, 2, 2, 3],
  'If process param., provide calc.': [1, 0, 1, 6],
  'Save output to file': [4, 0, 4, 0],
  'Understandable output tables': [5, 0, 3, 0],
  'Use seeds': [5, 0, 3, 0],
  'Code to make tables': [1, 1, 4, 2],
  'Code to make figures': [1, 2, 5, 0],
  'Code to process in-text results': [0, 0, 3, 5],
  'Run instructions': [2, 1, 5, 0],
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| | | | | | ❌ | | |

<!--TODO: Check if any other studies had commits after publication-->

@@

### Packages and versions

@@

### Packages

@@

### Versions

@@

### Summary

@@

### Provide code to process results into tables

@@

### Provide code to process results into figures

@@

### Provide code to calculate in-text results

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | ✅ | ✅ | ✅ |

@shoaib_simulation_2021: Fully met. Provided as a single `.py` file which ran model with function `main()`.

@huang_optimizing_2019: Not met. The model code was provided within the code for a web application, but the paper was not focused on this application, and instead on specific model scenarios. I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.

@lim_staff_2020: Fully met. Provided as a single `.py` file which ran the model with a for loop.

@kim_modelling_2021: Fully met. Has seperate `.R` scripts for each scenario which ran the model by calling functions from elsewhere in repository.

@anagnostou_facs-charm_2022: Fully met. Can run model from command line.

@johnson_cost_2021: Fully met. Model provided as a package (which is an R interface for the C++ model).

@hernandez_optimal_2015: Fully met. The model (python code) can be run from `main.py`.

@wood_value_2021: Fully met. Provided as a single `.R` file which ran the model with a for loop.

@@

@@

### State run time

@@

### State machine specification

@@

### Computationally expensive models

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | N/A | N/A | N/A | ❌ | N/A |

>>>>

It **excludes** the "Other section". It also excludes a few criteria which weren't felt particularly relevant/suitable to mark as met or not. These were "link publication to a specific version of the code", "optimise model run time" and "avoid large file sizes".

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
    'Share code with an open licence': [4, 0, 4, 0],
    'List required packages and versions': [0, 6, 2, 0],
    'Provide code for all scenarios<br>and sensitivity analyses': [1, 1, 5, 1],
    'Ensure model parameters are correct': [4, 2, 2, 0],
    'Control randomness': [5, 0, 3, 0],
    'Include code to calculate all<br>required model outputs': [3, 0, 5, 0],
    'Include code to generate the tables,<br>figures and other reported results': [1, 3, 4, 0],
    'Separate model code from applications': [1, 0, 1, 6],
    'Avoid hard-coded parameters': [3, 2, 2, 1],
    'Minimise code duplication': [5, 0, 3, 0],
    'Comment sufficiently': [1, 3, 4, 0],
    'Ensure clarity and consistency<br>in the model results tables': [5, 0, 3, 0],
    'Include run instructions': [2, 1, 5, 0],
    'State run times and<br>machine specifications': [0, 5, 3, 0],
    'Save output to a file': [4, 0, 4, 0],
    'Avoid excessive output files': [7, 0, 1, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

![](../images/reproduction_wheel.png)

@@

Whether or not they did it:

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ | ❌ |

Then, considering how "applicable" it feels... although you could argue those where I have marked "non-applicable" would become applicable with the addition of any new commits to the repository.

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | ❌ | N/A | N/A |

@shoaib_simulation_2021, @hernandez_optimal_2015: N/A. Not met but not an issue as last commit (with exception of any related to licence from our communication) is prior to publication, so marked as not applicable.

@huang_optimizing_2019, @lim_staff_2020, @anagnostou_facs-charm_2022, @wood_value_2021: N/A. Only 1 commit (excluding repo creation), or only commits on one day.

@kim_modelling_2021: Not met. Had commits to their GitHub repository after the publication date - though these largely appear related to a different model in the same repository, or for a fix.

@@

**Packages and versions**

@@

**Packages**

@@

**Versions**

@@

**Summary**

@@

**Provide code to process results into tables**

@@

**Provide code to process results into figures**

@@

**Provide code to calculate in-text results**

@@

![](../images/troubleshooting_wheel.png)

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | ❌ | N/A | N/A | ✅ | N/A | N/A | N/A |

For studies where this is relevant (i.e. with applications):

* @huang_optimizing_2019: Not met. The model code was provided within the code for a web application, but the paper was not focused on this application, and instead on specific model scenarios. I had to extract the model code and transform it into a format that was "runnable" as an R script/notebook.
* @anagnostou_charm_2022: Fully met. Code for web app in a seperate repository to model code.

For other studies, regarding whether the model code was in a "runnable" format and not embedded within anything else...

* @shoaib_simulation_2021: Provided as a single `.py` file which ran model with function `main()`.
* @lim_staff_2020: Provided as a single `.py` file which ran the model with a for loop.
* @kim_modelling_2021: Has seperate `.R` scripts for each scenario which ran the model by calling functions from elsewhere in repository.
* @johnson_cost_2021: Model provided as a package (which is an R interface for the C++ model).
* @hernandez_optimal_2015: The model (python code) can be run from `main.py`.
* @wood_value_2021: Provided as a single `.R` file which ran the model with a for loop.

@@

**Summary (whether stated both)**

@@

**State run time**

@@

**State machine specification**

@@

**Computationally expensive models**

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ✅ | ✅ | ✅ | ✅ | ✅ | ❌ | ✅ |
